Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}

### 2019-05-30 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Final version.

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{hyperref,xcolor}
\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{fig02.png}
\centering
\caption{Euler diagram of the different classifications of metaheuristics.} \label{fig02}
\end{figure}
\FloatBarrier

@@

Experiments are done in two groups with 30 independent runs for each. The source code originally is divided for test with star topology and incident nodes participation as migration strategies. That is why there are two groups of experiments. Each experiment compares pure Euclidean distance implementation and the proposed Hausdorff distance modification.

@@

Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so great, but as it is shown in Fig.\ref{fig04} when an incident nodes participation is used the proposed modification leads to convergence seep-up.

>>>>

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{hyperref,xcolor}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{listings}
\definecolor{very-light-gray}{gray}{0.95}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth,height=0.65\textwidth]{fig02.png}
\centering
\caption{Euler diagram of the different classifications of metaheuristics.} \label{fig02}
\end{figure}
%\FloatBarrier

@@

Experiments are done in two groups with 30 independent runs for each. The source code originally is divided for test with star topology and incident nodes participation as migration strategies. That is why there are two groups of experiments. Each experiment compares pure Euclidean distance implementation and the proposed Hausdorff distance modification. Parameters of the genetic algorithm are listed in Tab. \ref{tab01}.

\begin{table}
\caption{Genetic algorithm parameters.}
\label{tab01}
\begin{tabular}{p{6.9cm}p{4.4cm}}
\hline\noalign{\smallskip}
\textbf{Parameter} & \textbf{Value} \\
\hline\noalign{\smallskip}
generation gap & 0.93 \\
crossover rate & 0.98 \\
mutation rate & 0.01 \\
maximum generations & 10000 \\
number of individuals & 37 \\
number of variables & floating \\
inserted rate & 100 \% \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}
\FloatBarrier

@@

Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so great, but as it is shown in Fig.\ref{fig04} when an incident nodes participation is used the proposed modification leads to convergence seep-up. Calculation of a Euclidean distance between two cubes uses six calculations of the sides for the cube (Listing \ref{lst01}). In the case of Hausdorff distance there are six times more calls of a single Euclidean distance calculation (Listing \ref{lst02}).

\begin{lstlisting}[caption={Euclidean distance.},label={lst01},backgroundcolor=\color{very-light-gray},frame={single}]
double euclidean(const int side1[3][3], 
                 const int side2[3][3]) const {
  double distance = 0.0;

  for(int i=0; i<3; i++) {
    for(int j=0; j<3; j++) {
      distance += (side1[i][j]-side2[i][j]) * 
                  (side1[i][j]-side2[i][j]);
    }
  }

  return sqrt(distance);
}
\end{lstlisting}
\FloatBarrier

\begin{lstlisting}[caption={Hausdorff distance.},label={lst02},backgroundcolor=\color{very-light-gray},frame={single}]
double hausdorff(const RubiksCube &cube) const {
  double min[] = {INT_MAX, INT_MAX, INT_MAX, 
                  INT_MAX, INT_MAX, INT_MAX};

  for(int s1=0; s1<6; s1++) {
    for(int s2=0; s2<6; s2++) {
      double distance = 
      euclidean(*sides[s1], *(cube.sides)[s2]);

      if(min[s1] > distance) {
        min[s1] = distance;
      }
    }
  }

  double result = min[0];
  for(int s1=0; s1<6; s1++) {
    if(result < min[s1]) {
      result = min[s1];
    }
  }

  return(result);
}
\end{lstlisting}
\FloatBarrier
